---
title: "P3 WineQualityWhites"
author: ""
date: "20.4.2015"

output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---

#General Information about the dataset

Citation Request:
  This dataset is public available for research. The details are described in [Cortez et al., 2009]. 
  Please include this citation if you plan to use this database:

  P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. 
  Modeling wine preferences by data mining from physicochemical properties.
  In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.

  Available at: [@Elsevier] http://dx.doi.org/10.1016/j.dss.2009.05.016
                [Pre-press (pdf)] http://www3.dsi.uminho.pt/pcortez/winequality09.pdf
                [bib] http://www3.dsi.uminho.pt/pcortez/dss09.bib

1. Title: Wine Quality 

2. Sources
   Created by: Paulo Cortez (Univ. Minho), Antonio Cerdeira, Fernando Almeida, Telmo Matos and Jose Reis (CVRVV) @ 2009
   
3. Past Usage:

  P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. 
  Modeling wine preferences by data mining from physicochemical properties.
  In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.

  In the above reference, two datasets were created, using red and white wine samples.
  The inputs include objective tests (e.g. PH values) and the output is based on sensory data
  (median of at least 3 evaluations made by wine experts). Each expert graded the wine quality 
  between 0 (very bad) and 10 (very excellent). Several data mining methods were applied to model
  these datasets under a regression approach. The support vector machine model achieved the
  best results. Several metrics were computed: MAD, confusion matrix for a fixed error tolerance (T),
  etc. Also, we plot the relative importances of the input variables (as measured by a sensitivity
  analysis procedure).
 
4. Relevant Information:

   The two datasets are related to red and white variants of the Portuguese "Vinho Verde" wine.
   For more details, consult: http://www.vinhoverde.pt/en/ or the reference [Cortez et al., 2009].
   Due to privacy and logistic issues, only physicochemical (inputs) and sensory (the output) variables 
   are available (e.g. there is no data about grape types, wine brand, wine selling price, etc.).

   These datasets can be viewed as classification or regression tasks.
   The classes are ordered and not balanced (e.g. there are munch more normal wines than
   excellent or poor ones). Outlier detection algorithms could be used to detect the few excellent
   or poor wines. Also, we are not sure if all input variables are relevant. So
   it could be interesting to test feature selection methods. 

5. Number of Instances: red wine - 1599; white wine - 4898. 

6. Number of Attributes: 11 + output attribute
  
   Note: several of the attributes may be correlated, thus it makes sense to apply some sort of
   feature selection.

7. Attribute information:

   For more information, read [Cortez et al., 2009].

   Input variables (based on physicochemical tests):
   1 - fixed acidity (tartaric acid - g / dm^3)
   2 - volatile acidity (acetic acid - g / dm^3)
   3 - citric acid (g / dm^3)
   4 - residual sugar (g / dm^3)
   5 - chlorides (sodium chloride - g / dm^3
   6 - free sulfur dioxide (mg / dm^3)
   7 - total sulfur dioxide (mg / dm^3)
   8 - density (g / cm^3)
   9 - pH
   10 - sulphates (potassium sulphate - g / dm3)
   11 - alcohol (% by volume)
   Output variable (based on sensory data): 
   12 - quality (score between 0 and 10)

8. Missing Attribute Values: None

9. Description of attributes:

   1 - fixed acidity: most acids involved with wine or fixed or nonvolatile (do not evaporate readily)

   2 - volatile acidity: the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste

   3 - citric acid: found in small quantities, citric acid can add 'freshness' and flavor to wines

   4 - residual sugar: the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with
       greater than 45 grams/liter are considered sweet

   5 - chlorides: the amount of salt in the wine

   6 - free sulfur dioxide: the free form of SO2 exists in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents
       microbial growth and the oxidation of wine

   7 - total sulfur dioxide: amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations 
       over 50 ppm, SO2 becomes evident in the nose and taste of wine

   8 - density: the density of water is close to that of water depending on the percent alcohol and sugar content

   9 - pH: describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale

   10 - sulphates: a wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant

   11 - alcohol: the percent alcohol content of the wine

   Output variable (based on sensory data): 
   12 - quality (score between 0 and 10)

<hr>
#Univariate Plots
Short overview of the used data:
```{r, echo=FALSE}
library(ggthemes)
wqw<-read.csv('wineQualityWhites.csv', sep=',')
wqw$qual<-(wqw$quality)
wqw$quality<-as.factor(wqw$quality)

#dummy<-model.matrix(~ quality - 1, data=wqw)
#wqw<-cbind(wqw,dummy)
dim(wqw)
names(wqw)
str(wqw)
summary(wqw)
```
The worst quality is 3, the best quality is 9 in the dataset, to get a better understanding of the quality ranking we plot a histogram.

```{r, echo=FALSE}
ggplot(aes(x=as.numeric(quality)), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.99)+
  ggtitle('Histogramm for quality')
table(wqw$quality)
```

The most values are in quality group nr. 5 and 6
In our analysis we try find a linear model to estimate the quality of the wine from the given parameter.
To do the fact that we have different number for each qulity group I would like to plot histograms four each group.
<hr>

```{r, echo=FALSE}
ggplot(aes(x=alcohol), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.2)+
  scale_x_continuous(lim=c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for alcohol for each factor quality - within limits 1% quantile and 99% quantile')

#table(wqw$alcohol)

ggplot(aes(x=alcohol), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.2)+
  scale_x_continuous(lim=c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99)))


```

It looks like that good quality wines have less alcohol than bad quality wines, we will check later by calculating the mean.
<hr>

```{r, echo=FALSE}
ggplot(aes(x=pH), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.01)+
  scale_x_continuous(lim=c(quantile(wqw$pH,0.01), quantile(wqw$pH,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for pH for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=pH), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.01)+
  scale_x_continuous(lim=c(quantile(wqw$pH,0.01), quantile(wqw$pH,0.99)))
table(wqw$pH)
```

From the pH distribution I cant see any trends in the quality group.
<hr>

```{r, echo=FALSE}
ggplot(aes(x=density), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.0006)+
  scale_x_continuous(lim=c(quantile(wqw$density,0.01),quantile(wqw$density,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for density for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=density), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.0006)+
  scale_x_continuous(lim=c(quantile(wqw$density,0.01),quantile(wqw$density,0.99)))
```

Good wines tend to have density of 1, bad ones tend to 0.99
<hr>


```{r, echo=FALSE}
ggplot(aes(x=chlorides), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.001)+
  scale_x_continuous(lim=c(quantile(wqw$chlorides,0.01),quantile(wqw$chlorides,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for chlorides for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=chlorides), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.001)+
  scale_x_continuous(lim=c(quantile(wqw$chlorides,0.01),quantile(wqw$chlorides,0.99)))
```

The chlorides distribution looks pretty much the same in each group.
<hr>

```{r, echo=FALSE}
ggplot(aes(x=sulphates), data=wqw)+
  geom_histogram(colour = "black",fill = "white",binwidth=0.02)+
  scale_x_continuous(lim=c(quantile(wqw$sulphates,0.01),quantile(wqw$sulphates,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for sulphates for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=sulphates), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.02)+
  scale_x_continuous(lim=c(quantile(wqw$sulphates,0.01),quantile(wqw$sulphates,0.99)))

table(wqw$sulphates)
```

For sulphates applies the same.
<hr>

```{r, echo=FALSE}
ggplot(aes(x=total.sulfur.dioxide), data=wqw)+
  geom_histogram(colour = "black",fill = "white")+
  scale_x_continuous(lim=c(quantile(wqw$total.sulfur.dioxide,0.01),quantile(wqw$sulfur.dioxide,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for total.sulfur.dioxide for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=total.sulfur.dioxide), data=wqw)+
  geom_histogram(colour = "black",fill = "white")+
  scale_x_continuous(lim=c(quantile(wqw$total.sulfur.dioxide,0.01),quantile(wqw$sulfur.dioxide,0.99)))
```

<hr>

```{r, echo=FALSE}
ggplot(aes(x=free.sulfur.dioxide), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=1)+
  scale_x_continuous(lim=c(quantile(wqw$free.sulfur.dioxide,0.01), quantile(wqw$free.sulfur.dioxide,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for free.sulfur.dioxide for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=free.sulfur.dioxide), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=1)+
  scale_x_continuous(lim=c(quantile(wqw$free.sulfur.dioxide,0.01), quantile(wqw$free.sulfur.dioxide,0.99)))
```
<hr>


```{r, echo=FALSE}
ggplot(aes(x=residual.sugar), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.2)+
  scale_x_continuous(lim=c(0,quantile(wqw$residual.sugar,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for residual.suagr for each factor quality - within limits 1% quantile and 99% quantile')

head(table(wqw$residual.sugar))

ggplot(aes(x=residual.sugar), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.2)+
  scale_x_continuous(lim=c(0,quantile(wqw$residual.sugar,0.99)))
```
<hr>

You can see that there are approximatley 50% of the values between 0.8 and 0.9, looks interesting.<br>
<br>
Using log10 transformation we can see two classes of whine, one with less sugar and another group with more sugar.<br>
You can find this density in all quality group, looks like the sweetness on its own is no quality mark.


```{r, echo=FALSE}
ggplot(aes(x=residual.sugar), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.2)+
  scale_x_log10()
```

```{r, echo=FALSE}
ggplot(aes(x=citric.acid), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.02)+
  scale_x_continuous(lim=c(quantile(wqw$citric.acid,0.01),quantile(wqw$citric.acid,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for factor citric.acid for each factor qulity - within limits 1% quantile and 99% quantile')

ggplot(aes(x=citric.acid), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.02)+
  scale_x_continuous(lim=c(quantile(wqw$citric.acid,0.01),quantile(wqw$citric.acid,0.99)))
(table(wqw$citric.acid))
```

Here it is very interesting that we have these spike at level 0.49, maybe we can find the reason for that.



<hr>

```{r, echo=FALSE}
ggplot(aes(x=volatile.acidity), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.011)+
  scale_x_continuous(lim=c(quantile(wqw$volatile.acidity,0.01),quantile(wqw$volatile.acidity,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for volatile.acidity for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=volatile.acidity), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.011)+
  scale_x_continuous(lim=c(quantile(wqw$volatile.acidity,0.01),quantile(wqw$volatile.acidity,0.99)))
```
<hr>

```{r, echo=FALSE}
ggplot(aes(x=fixed.acidity), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.11)+
  scale_x_continuous(lim=c(quantile(wqw$fixed.acidity,0.01),quantile(wqw$fixed.acidity,0.99)))+
  facet_wrap(~quality)+ 
  theme(plot.title = element_text(size = 10))+
  ggtitle('Histogramms for fixed.acidity for each factor quality - within limits 1% quantile and 99% quantile')

ggplot(aes(x=fixed.acidity), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.11)+
  scale_x_continuous(lim=c(quantile(wqw$fixed.acidity,0.01),quantile(wqw$fixed.acidity,0.99)))
```

```{r, echo=FALSE}

```

Calculating the mean values for each quality group.

```{r, echo=FALSE}
library(dplyr)
wqw_sum<- wqw %>%
  group_by(quality) %>%
  summarise(mean_alcohol = mean(alcohol),
            mean_pH = mean(pH),
            mean_density = mean(density),
            mean_chlorides = mean(chlorides),
            mean_sulphates = mean(sulphates)) %>%
  ungroup() %>%
  arrange(quality)
wqw_sum

wqw_sum2<- wqw %>%
  group_by(quality) %>%
  summarise(mean_t.sulfur.diox. = mean(total.sulfur.dioxide),
            mean_f.sulfur.diox. = mean(free.sulfur.dioxide),
            mean_r.sugar. = mean(residual.sugar)) %>%
  ungroup() %>%
  arrange(quality)
wqw_sum2

wqw_sum3<- wqw %>%
  group_by(quality) %>%
  summarise(mean_citric.acid. = mean(citric.acid),
            mean_vol.acidity. = mean(volatile.acidity),
            mean_fix.acidity. = mean(fixed.acidity),
            n=n()) %>%
  ungroup() %>%
  arrange(quality)
wqw_sum3
```

You can see the mean values for alcohol, very good wines have 10 %, very bad wines have 12 % <br>
From the pH value you can say better wines are more sour.<br>
Good wines tend to have density of 1, bad ones tend to 0.99 <br>
The chlorides group show that bad wines have higher value than better one.<br>
<br>
Later we will look at more detail

<hr>
#Univariate Analysis
##What is the structure of your dataset?

There are 4898 different red wine variants with 13 features:
<ul>
<li> fixed acidity -> fa
<li> volatile acidity -> va
<li> critic acid -> ca
<li> residual sugar -> rs
<li> chlorides -> c
<li> free sulfur dioxide -> fsd
<li> total sulfur dioxide -> tsd
<li> density -> d
<li> pH -> p
<li> sulphates -> s
<li> alcohol -> a
<li> quality -> q
</ul>

The variable quality is ordered factor variables with the following levels.

(worst) ... (best)<br>
quality: 0, 1, 2 ,3, 4, 5, 6, 7, 8, 9, 10
<hr>
##Other observations:
The median of the quality is 6.
In alcohol there is a spike at 9.5
in residual sugar there is also a spike at 2.

If you look back to the quality data
we saw that 1457 white wines get quality 5, 2198 wines get a 6 and 880 wines get a 7.
Now it is interesting to see that the distribution for quality is skewed.

The distribution for alcohol, sulphates, chlorides, residual sugar, volatile acidity are also skewed. That is my objective opinion by looking to the distribition charts.
<hr>
##What is/are the main feature(s) of interest in your dataset?
What I know as a wine "expert" pH, alcohol and sugar has a big impact to the wine quality. So I gess this parameters should have the most impact to the predictive model to quality of white wine, thats my personal opinion.
<hr>
##What other features in the dataset do you think will help support your investigation into your feature(s) of interest?
By comparing the distributions and mean values it could be that chlorides and density has an impact on quality.
<hr>
##Did you create any new variables from existing variables in the dataset?
First I changed the type of the variable quality from int to factor. In the dataset quality is the only categorical factor.

<hr>
##Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to dplyr, adjust, or change the form of the data? If so, why did you do this?
The histogram for the variable critic.acid strainge because there is a spike at level 0.5<br>
I used dplyr to group the values per quality and calulate the mean values for some choosen parameter.<br>
I plot the data between the quantiles 1% and 99% to increase some huge spikes in the plot.<br>
For the parameter residual.sugar I used log10 transformation, to show that there are two group of whines.

<hr>
#Bivariate Plots Section

For a quick overview we created a correlation plot from all parameters:

```{r, echo=FALSE}

library(lattice)
levelplot(cor(wqw[,c(2:12,14)]), xlab="", ylab="", scales=list(x=list(rot=90) ))                                                                                                                                                                                                      
```

Here are the parameter that have the highest correlation with quality:
<ul>
<li> fixed acidity
<li> volatile acidity
<li> residual sugar
<li> chlorides
<li> total sulfur dioxide
<li> density
<li> alcohol
</ul>


The highest correlation is between residual.sugar and density<br>
In the univariate capitel we saw that values of parameters changes in the different groups. Now we try to find some relations between the different parameters.

```{r, echo=FALSE}
cor(wqw[,c(2:12,14)])

library(GGally)
library(corrplot)
cex.before <- par("cex")
par(cex = 0.7)
corrplot(cor(wqw[,c(2:12,14)]),  method = "number", cex.col=0.12, cex.var=0.13, order = "AOE", tl.cex = 1/par("cex"),
    cl.cex = 1/par("cex"), addCoefasPercent = TRUE)


```

The high positive correlation we can find between free.sulfur.dioxide, total.sulfur.dioxide, residual.sugar and density and on the other site negative correlations between alcohol and total.sulfur.dioxide, residual.sugar, density and chlorides.


<br>In the next step we will check the scatterplot of the four highest correlations.
<br>

```{r, echo=FALSE}
ggplot(data = wqw, aes(x = alcohol, y =density )) +
  geom_jitter(alpha=1/4, shape=21)+
  scale_x_continuous(lim=c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99)))+
  scale_y_continuous(lim=c(quantile(wqw$density,0.01),quantile(wqw$density,0.99)))+
  geom_smooth(method='lm', color='red')
cor(wqw$ alcohol, wqw$density)

ggplot(data = wqw, aes(x = total.sulfur.dioxide, y = free.sulfur.dioxide)) +
  geom_jitter(alpha=1/4, shape=21)+
  scale_x_continuous(lim=c(quantile(wqw$total.sulfur.dioxide,0.01),quantile(wqw$total.sulfur.dioxide,0.99)))+
  scale_y_continuous(lim=c(quantile(wqw$free.sulfur.dioxide,0.01),quantile(wqw$free.sulfur.dioxide,0.99)))+
  geom_smooth(method='lm', color='red')
cor(wqw$total.sulfur.dioxide, wqw$free.sulfur.dioxide)

ggplot(data = wqw, aes(x = residual.sugar, y = density)) +
  geom_jitter(alpha=1/4, shape=21)+
  scale_x_continuous(lim=c(quantile(wqw$residual.sugar,0.01),quantile(wqw$residual.sugar,0.99)))+
  scale_y_continuous(lim=c(quantile(wqw$density,0.01),quantile(wqw$density,0.99)))+
  geom_smooth(method='lm', color='red')
cor(wqw$residual.sugar, wqw$density)

ggplot(data = wqw, aes(x = qual, y = alcohol)) +
  geom_jitter(alpha=1/4, shape=21)+
  scale_x_continuous(lim=c(quantile(wqw$qual,0.01),quantile(wqw$qual,0.99)))+
  scale_y_continuous(lim=c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99)))+
  geom_smooth(method='lm', color='red')
cor(wqw$density, wqw$qual)
  
```

The biggest impact for quality is density (negative correlated) and alcohol (positive correlated), for that we will make a Boxplot

```{r, echo=FALSE}
ggplot(aes(x = quality, y = density), data = wqw) + 
  geom_boxplot()+  
  stat_summary(fun.y=mean,geom='point', shape=4)+
  ggtitle('Boxplot')
```

As shown in the univariate section bad wines have a higher density than good wines.

```{r, echo=FALSE}
ggplot(aes(x = quality, y = alcohol), data = wqw) + 
  geom_boxplot()+  
  stat_summary(fun.y=mean,geom='point', shape=4)+
  ggtitle('Boxplot')
```

Bad wines have less alcohol compared to good wines

<hr>



#Bivariate Analysis
##Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

residual.sugar and density has a high positive correlation, comparted to the other correlation factor, so I will reject one of this parameter for a linear model.

There is a very strong negative correlation between alcohol and density of -0.78

Quality has correlations to density, chlorides, volatile.acidity and alcohol.

<hr>
##Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

The dataset has a high number for quality nr. 5 and nr. 6
I was wondering that pH have not more impact on quality
<hr>
##What was the strongest relationship you found?
The strongest relationship for building a model to predict the quality of red wine is alcohol with correlation 0.44

#Multivariate Plots Section
<hr>

In the first graph we show the alcohol for each quality group in one chart
```{r, echo=FALSE}
ggplot(aes(x=alcohol), data=wqw)+
  geom_histogram(aes(fill=quality), binwidth=0.2)+
  scale_fill_brewer(type = 'qual')
library(RColorBrewer)
#ggplot(aes(x = alcohol, y = density), data = wqw) + 
#  geom_point(aes(colour=quality),alpha = 0.5, shape=19, position = 'jitter') +  
#  scale_x_continuous(limits = c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99))) + 
#  scale_y_continuous(limits = c(quantile(wqw$density,0.01),quantile(wqw$density,0.99))) +
#  ggtitle('Scatterplot alcohol versus density')
```


To show the interesting relationship between alcohol, density and quality on one hand and residual.sugar, density and quality on the other hand we make this plot. 
```{r, echo=FALSE}
library(gridExtra)
a<-ggplot(aes(x=alcohol, y=density), data=wqw)+
  geom_point(aes(color=quality),alpha=.3, size = 5)+
  scale_x_continuous(limits = c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99))) + 
  scale_y_continuous(limits = c(quantile(wqw$density,0.01),quantile(wqw$density,0.99))) +
  geom_smooth(method='lm', color='red')
b<-ggplot(aes(x=residual.sugar, y=density), data=wqw)+
  geom_point(aes(color=quality),alpha=.3, size = 5)+
  scale_x_continuous(limits = c(quantile(wqw$residual.sugar,0.01),quantile(wqw$residual.sugar,0.99))) + 
  scale_y_continuous(limits = c(quantile(wqw$density,0.01),quantile(wqw$density,0.99)))  +
  geom_smooth(method='lm', color='red')
grid.arrange(arrangeGrob(a,b, ncol=1, nrow=2), main = "density function for alcohol and density",nrow=1)
```

```{r, echo=FALSE}
#ggplot(aes(x=volatile.acidity, y=citric.acid), data=wqw)+
#  geom_point(aes(color=quality),alpha=.3, size = 5)+
#  scale_x_continuous(limits = c(quantile(wqw$volatile.acidity,0.01),quantile(wqw$volatile.acidity,0.99))) + 
#  scale_y_continuous(limits = c(quantile(wqw$citric.acid,0.01),quantile(wqw$citric.acid,0.99))) 
 ```

```{r, echo=FALSE}
#ggplot(aes(x=total.sulfur.dioxide, y=free.sulfur.dioxide), data=wqw)+
#  geom_point(aes(color=quality),alpha=.3, size = 5)+
#  scale_x_continuous(limits = c(quantile(wqw$total.sulfur.dioxide,0.01),quantile(wqw$total.sulfur.dioxide,0.99))) + 
#  scale_y_continuous(limits = c(quantile(wqw$free.sulfur.dioxide,0.01),quantile(wqw$free.sulfur.dioxide,0.99))) 
```

To answer the question how sugar impact on alcohol and density, see next plot.

```{r, echo=FALSE}
ggplot(aes(x=density, y=alcohol), data=wqw)+
  geom_point(aes(color=residual.sugar),alpha=.3, size = 5)+
  scale_x_continuous(limits = c(quantile(wqw$density,0.01),quantile(wqw$density,0.99))) + 
  scale_y_continuous(limits = c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99))) 
```

```{r, echo=FALSE}
#ggplot(aes(x=(volatile.acidity), y=alcohol), data=wqw)+
#  geom_point(aes(color=quality),alpha=.3, size = 5)+
#  scale_x_continuous(limits = c(quantile(wqw$volatile.acidity,0.01),quantile(wqw$volatile.acidity,0.99))) + 
#  scale_y_continuous(limits = c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99))) +
#  geom_smooth(method='lm', color='red')
```

In the last picture I will show the density function for alcohol, pH, density and chlorides to show grafically what we did in the end of the Univariaty Analysis by using the group function 

```{r, echo=FALSE}
library(gridExtra)
a<-ggplot(aes(x=alcohol), data=wqw)+
  geom_density(aes(fill=quality),alpha=.3)
b<-ggplot(aes(x=pH*10), data=wqw)+
  geom_density(aes(fill=quality),alpha=.3)
c<-ggplot(aes(x=density), data=wqw)+
  geom_density(aes(fill=quality),alpha=.3)+
  scale_x_continuous(limits = c(quantile(wqw$density,0.01),quantile(wqw$density,0.999)))
d<-ggplot(aes(x=chlorides), data=wqw)+
  geom_density(aes(fill=quality),alpha=.3)+
  scale_x_continuous(limits = c(quantile(wqw$chlorides,0.01),quantile(wqw$chlorides,0.97)))

grid.arrange(arrangeGrob(a,b,c,d, ncol=2, nrow=2), main = "density functions",nrow=1)
```

From my investigation I would choose the variables alcohol and volatile.acidity to build a linear modell to predict quality. If you compare that modell to the linear model that uses all parameter, we can descripte with our two parameter as much.

```{r, echo=FALSE}
library(memisc)
lin<-lm( formula= as.numeric(quality)~alcohol, data=wqw[,2:13])
lin2<-update(lin,~.+volatile.acidity)

mtable(lin, lin2)


summary(lm( formula= as.numeric(quality)~., data=wqw[,2:13]))
```
#Multivariate Analysis
##Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?
The most important parameter for predicting quality is alcohol and volatile.acidity that will be shown in the linear model.

##Were there any interesting or surprising interactions between features?
Yes it was very surprising that all high correlated parameter with quality has a high correlation with alcohol, for example <br>
quality <-> total.sulfur.dioxide <-> alcohol <br>
quality <-> density <-> alcohol <br>
quality <-> chlorides <-> alcohol <br>

##OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.
Yes I build a linear model with the paramter alcohol and volatile.acidity.

The linear model has a  R-squared of  0.24, that is very bad.

<hr>

#Final Plots and Summary

###Plot One


```{r, echo=FALSE}
ggplot(aes(x=residual.sugar), data=wqw)+
  geom_histogram(colour = "black",fill = "white", binwidth=0.05)+
  scale_x_log10()+
  ggtitle('log10 residual.sugar')
```


###Description One

The distribution of residual.sugar appears to be bimodal, there are two groups of sweetness of wihte wines in all quality groups. This graph is very interasting because by using of transformations you get more information.
<hr>

###Plot Two
```{r, echo=FALSE}
cex.before <- par("cex")
par(cex = 0.7)
corrplot(cor(wqw[,c(2:12,14)]),  method = "number", cex.col=0.12, cex.var=0.13, order = "AOE", tl.cex = 1/par("cex"),
    cl.cex = 1/par("cex"), addCoefasPercent = TRUE)
```

###Description Two
The plot shows the correlationmatrix of all parameters in the dataset, it is a very important graph for further analysis.
<hr>

###Plot Three

```{r, echo=FALSE}
ggplot(aes(x=density, y=alcohol), data=wqw)+
  geom_point(aes(color=residual.sugar),alpha=.3, size = 5)+
  scale_x_continuous(limits = c(quantile(wqw$density,0.01),quantile(wqw$density,0.99))) + 
  scale_y_continuous(limits = c(quantile(wqw$alcohol,0.01),quantile(wqw$alcohol,0.99))) +
  ggtitle('Scatterplot from three variables')+
  geom_smooth(method='lm', color='red')
```

###Description Three

There is a high negative correlation between density and alcohol of -0.78, white wines with more alcohol have less sugar than wines with less alcohol, wines with density araound 1 have more residual.sugar than with density around 0.99
<hr>

#Reflection

It was a nice experience to work with that dataset. At the beginning I was happy to deal with no factors, on a second look I realized that the variable quality is a factor but it is used as integer. First I plot all histograms to get an idea of the dataset. There are ten different quality factors; this dataset uses only three (meaning that for three different categories more than 800 data’s are available). The second part analyzes the correlations; I was very surprised that alcohol and quality have a high correlation to the same parameters. That makes it very hard to find the parameters for a linear model. First I thought pH, sugar and alcohol are the main parameters but the data tell a different story. By choosing the parameter alcohol and, volatile.acidity I created a linear model with R-squared of 0.24 - that’s a very bad result. 
Reasons for that could be that the dataset has too less values for the different quality categories to get a representative result or the objective parameter quality does not fit with the chemical parameters. It would be very interesting to get a dataset with more data per quality.


<hr>
<hr>





